Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-12-28 awipev-CO2.Rmd
text maintenance TA
pH seaFET discrete data + shading period dygraph added

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                       ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07, NA ))))))))

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
  geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank())

@@

plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
  annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_dur), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank())

@@

###**TA analyser**
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

>>>>

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 09, NA )))))))))))

@@

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

@@

plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
  geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))

@@

plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
  annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_dur), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))

@@

###**TA analyser**
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.                  
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
